---
title: "Quarto Practice"
format: html
editor: visual
execute: 
  warning: false
---

Suppressing warnings and messages just for this code chunk

```{r}
#| warning: false
#| message: false
library(tidyverse)
```

running code but now showing code or output

```{r}
#| include: false
#return first 6 lines of stawars data
head(starwars)

#return dimentions of star wars data
dim(starwars)
```

Showing output but no code

```{r}
#| warning: false
#| echo: false
ggplot(data = starwars, aes(x= height, y= mass, color = mass)) + 
  geom_point() + labs(x = "Height (cm)", 
       y = "Mass (kg)")
```

Show only code and output.

```{r}
#| warning: false
#| fig-cap: "Caption text"
#| fig-alt: "alt text"
ggplot(data = starwars, aes(x= height)) + 
  geom_histogram(color = "blue", fill = "purple")
```

find summary stats for Starwars characters

```{r}
sw_height_mean <- mean(starwars$height, na.rm = TRUE)
sw_height_median <- median(starwars$height, na.rm = TRUE)
sw_height_var <- var(starwars$height, na.rm = TRUE)
sw_height_sd <- sd(starwars$height, na.rm = TRUE)


```

The mean height of the characters in star wars is `r round(sw_height_mean, 1)` centimeters.

The median height of the characters in star wars is `r round(sw_height_median, 1)` centimeters.

The variance height of the characters in star wars is `r round(sw_height_var, 1)` centimeters.

The standard deviation height of the characters in star wars is `r round(sw_height_sd, 1)` centimeters.
